---
title: "ROI study 2023"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: hide
    theme: lumen
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---


```{r setup, include = F}
knitr::opts_chunk$set(echo = TRUE, 
               warning = FALSE,
               message = FALSE,
               fig.path='figures/',
               fig.width = 7, 
               fig.height = 5)
options(DT.options = list(pageLength = 100, language = list(search = 'Filter:')))

knitr::opts_knit$set(root.dir = '~/Library/CloudStorage/GoogleDrive-mhawrilenko@springhealth.com/Shared drives/Data Science/people/matt/ds_git/ds_research_roi_study_2023/code')
```


```{r load-packages, message = FALSE, results = 'hide'}
# load packages
library(knitr)
library(tidyverse)
library(nerdify)
library(janitor)
library(rio)
library(lubridate)
library(table1)
library(lme4)
library(lmerTest)
library(lmeresampler)
library(car)
library(sjPlot)
library(ggplot2)
library(ggrepel)
library(marginaleffects)
library(see)
library(kableExtra)
library(gt)
```


# Load data and functions

## Load data 
``` {r load-data}

# Customers included in the study
customer_name <- c("Wellstar", "Pepsi", "Hearst", "Docusign", "Tegna")

# Make some lists to fill up
data_funnel <- list()
df_care_use <- list()
df_appts <- list()

# Get datasets that have not yet been concatenated
for (i in 1:length(customer_name)) {
# Load data
data_funnel[[i]] <- readRDS(paste0(Sys.getenv("claims_folder_path"), "data/round_2_analysis/", customer_name[i], "/", customer_name[i], "_data_funnel.Rdata")) %>%
  mutate(customer_name = customer_name[i]) 
df_care_use[[i]] <- readRDS(paste0(Sys.getenv("claims_folder_path"), "data/round_2_analysis/", customer_name[i], "/", customer_name[i], "_care_use.Rdata"))
df_appts[[i]] <- readRDS(paste0(Sys.getenv("claims_folder_path"), "data/round_2_analysis/", customer_name[i], "/", customer_name[i], "_appts_by_month.Rdata"))
}

# Now bind into a single df
data_funnel <- data_funnel %>% bind_rows()
df_care_use <- df_care_use %>% bind_rows()
df_appts <- df_appts %>% bind_rows()

# Now the dfs that have previously been concatenated
df_analyze_all <- readRDS(paste0(Sys.getenv("claims_folder_path"), "data/roi_study_2023/df_analyze_all.Rdata"))
df_matched <- readRDS(paste0(Sys.getenv("claims_folder_path"), "data/roi_study_2023/df_matched.Rdata"))

```



# Analyze utilization pre and post launch
Spring promises to drive value by getting more people into care who otherwise would never have received it. Here, we test this premise by determining how much mental health treatment utilization changed after Spring launched. Here, we examine 3 metrics:  
  1. How annual outpatient behavioral health treatment utilization changed pre and post Spring  
  2. Any utilization by month  
  3. Number of sessions per month 
  
  
## Annual utilization
The figure below shows that the proportion of any member receiving outpatient behavioral health care in the year prior to launch was X, and in the year post-launch was X. During the post launch year, Spring accounted for an increase of Z appointments over the carrier alone.
``` {r annual-utilization}
df_phase_summary <- df_care_use %>%
  filter(month_year >= baseline_start_date) %>%
  filter(month_year <= spring_end_date) %>%
  mutate(phase = ifelse(month_year < spring_start_date, "Pre-launch", "Post-launch")) %>%
  mutate(phase = factor(phase, levels = c("Pre-launch", "Post-launch"))) %>%
  group_by(customer_name, carrier_member_id, phase) %>%
  summarize(
    carrier_tx_count_month = sum(carrier_tx_count_month),
    spring_tx_count_month = sum(spring_tx_count_month),
    carrier_therapist_count_month = sum(carrier_therapist_count_month),
    spring_therapist_count_month = sum(spring_therapist_count_month)
  ) %>%
  ungroup()

care_use_table <- df_phase_summary %>%
  mutate(
    mh_appt_group = factor(case_when(
      carrier_tx_count_month > 0 & spring_tx_count_month > 0 ~ "Both Spring and Health Plan",
      carrier_tx_count_month > 0 & spring_tx_count_month == 0 ~ "Health Plan only",
      carrier_tx_count_month == 0 & spring_tx_count_month > 0 ~ "Spring only",
      carrier_tx_count_month == 0 & spring_tx_count_month == 0 ~ "No appointments"
    ),
    levels = c("Spring only", "Both Spring and Health Plan", "Health Plan only", "No appointments")
    )) %>%
  group_by(phase, mh_appt_group) %>%
  summarize(group_n = n()) %>%
  group_by(phase) %>%
  mutate(proportion = group_n/sum(group_n)) %>%
  mutate(across(group_n:proportion, ~ round(.x*100, 1))) %>%
  filter(mh_appt_group != "No appointments")

# Plot
color_scheme <- c("#37837c","#A9DbD6", '#c7c7c7')
  
ggplot(care_use_table, aes(x = phase, y=proportion, group = mh_appt_group, fill = mh_appt_group)) +
  geom_bar(position="stack", stat="identity", width = 0.5) +
  scale_fill_manual(values = color_scheme, name = "Provider") +
  geom_text(aes(label=proportion), position = position_stack(vjust = 0.5), colour = "black") +
  theme_modern() +
  labs(
    title = "Members using any outpatient behavioral health care in the year",
    x = "",
    y = "Percent",
    group = "",
    fill = ""
  )

```

  
  
## Plot 1: monthly utilization
Let's look at this at a more granular level. The figure below is consistent with the notion that Spring expanded access to mental health care in `r customer_name`'s population.


``` {r cust-avg-utilization, fig.width = 10, fig.height = 5}

care_use_avg <- df_phase_summary %>%
  mutate(
    mh_appt_group = factor(case_when(
      carrier_tx_count_month > 0 & spring_tx_count_month > 0 ~ "Both Spring and Health Plan",
      carrier_tx_count_month > 0 & spring_tx_count_month == 0 ~ "Health Plan only",
      carrier_tx_count_month == 0 & spring_tx_count_month > 0 ~ "Spring only",
      carrier_tx_count_month == 0 & spring_tx_count_month == 0 ~ "No appointments"
    ),
    levels = c("Spring only", "Both Spring and Health Plan", "Health Plan only", "No appointments")
    )) %>%
  group_by(customer_name, phase, mh_appt_group) %>%
  summarize(group_n = n()) %>%
  group_by(customer_name, phase) %>%
  mutate(proportion = group_n/sum(group_n)) %>%
  filter(mh_appt_group != "No appointments") %>%
  group_by(phase, mh_appt_group) %>%
  summarize(proportion = mean(proportion)) %>%
  mutate(proportion = round(100*proportion, 1))
  

# Plot
ggplot(care_use_avg, aes(x = phase, y=proportion, group = mh_appt_group, fill = mh_appt_group)) +
  geom_bar(position="stack", stat="identity", width = 0.5) +
  scale_fill_manual(values = color_scheme, name = "Provider") +
  geom_text(aes(label=proportion), position = position_stack(vjust = 0.5), colour = "black") +
  theme_modern() +
  labs(
    title = "Members using any outpatient behavioral health care in the year",
    x = "",
    y = "Percent",
    group = "",
    fill = ""
  )


# Monthly utilization
plot_monthly_avg <- df_care_use %>%
  filter(month_year >= baseline_start_date) %>%
  filter(month_year <= spring_end_date) %>%
  mutate(
    months_std = case_when(
      month_year < spring_start_date ~ interval(spring_start_date, month_year) %/% months(1),
      month_year >= spring_start_date ~ interval(spring_start_date, month_year) %/% months(1) + 1
    ),
    phase = ifelse(month_year < spring_start_date, "Pre-launch", "Post-launch"),
    provider = "Spring"
    ) %>%
  group_by(customer_name, mh_appt_group, months_std) %>%
  summarize(
    mh_appt_in_month = sum(mh_appt_in_month == "yes"),
    group_n = n()
    ) %>%
  group_by(customer_name, months_std) %>%
  mutate(n = sum(group_n)) %>%
  mutate(
    mh_appt_in_month_proportion = mh_appt_in_month/n,
    mh_appt_group = case_when(
      mh_appt_group == "Carrier only" ~ "Health Plan only",
      mh_appt_group == "Both Spring and Carrier" ~ "Both Spring and Health Plan",
      TRUE ~ mh_appt_group)
    ) %>%
  mutate(mh_appt_group = factor(mh_appt_group, levels = c("Spring only", "Both Spring and Health Plan", "Health Plan only"))) %>%
  filter(mh_appt_group != "No appointments") %>%
  group_by(months_std, mh_appt_group) %>%
  summarize(mh_appt_in_month_proportion = mean(mh_appt_in_month_proportion)) %>%
  arrange(mh_appt_group, months_std)


## Plot

## Make some plotting locations
pre_mean_avg <- round(
  sum(plot_monthly_avg$mh_appt_in_month_proportion[plot_monthly_avg$months_std < 0])/12, 
  3)
post_mean_avg <- round(
  sum(plot_monthly_avg$mh_appt_in_month_proportion[plot_monthly_avg$months_std > 0])/12,
  3)
max_avg <-max(
  plot_monthly_avg %>%
    group_by(months_std) %>%
    summarize(apps_in_month = sum(mh_appt_in_month_proportion)) %>%
    pull(apps_in_month)
)

## Plot
ggplot(plot_monthly_avg, aes(x = months_std, y=mh_appt_in_month_proportion, group = mh_appt_group, fill = mh_appt_group)) +
  geom_bar(position="stack", stat="identity") +
  scale_fill_manual(values = color_scheme, name = "Provider") +
  theme_modern() +
  geom_hline(yintercept = pre_mean_avg, linetype = "dashed") +
  geom_vline(xintercept = 0, color = "#48ADA3", linetype = "dashed") +
  theme(axis.text.x = element_text(angle = 70, vjust = 1, hjust=1)) +
  annotate(geom = "text", x = 3, y = max_avg*1.4, label = "Spring launch", color = "#37837c", size = 5) +
  annotate(geom = "text", x = -6.5, y = pre_mean_avg*1.2, label = paste0("Pre-launch = ", 100*pre_mean_avg, "% per month"), color = "#767676", size = 4) +
  annotate(geom = "text", x = 6.5, y = post_mean_avg*1.2, label = paste0("Post-launch = ", 100*post_mean_avg, "% per month"), color = "#37837c", size = 4) +
  labs(
    title = "Employees with at least 1 MH appointment",
    x = "Months from Spring launch",
    y = "Proportion"
  )

```

# Cohort comparisons
To determine Spring's impact on `r customer_name`'s total cost of care, we conducted a matching study. We identified the group of people who engaged with a Spring provider, a risk-matched group that did not use Spring, and compared the spend of both groups. Research demonstrates that spend increases at the time of a mental health diagnosis, so we compared changes in each group's spending from the year prior to receiving a MH diagnosis to the year after receiving a diagnosis, using a difference-in-differences design. 
  
  
## Data funnel
This table shows each step where participants were funneled into the analytic sample.
```{r data-funnel}

match_funnel <- df_matched %>% 
  group_by(spring_dummy) %>%
  summarize(
    n = n_distinct(carrier_member_id),
    filter_name = "Maintained in matching study"
    ) %>%
  mutate(total_n = sum(n)) %>%
  pivot_wider(
    id_cols = c(filter_name, total_n),
    names_from = spring_dummy,
    values_from = n
  ) 

data_funnel %>%
  group_by(filter_name) %>%
  summarize(across(-customer_name, sum)) %>%
  rbind(match_funnel) %>%
  arrange(-total_n) %>%
  kbl(caption = "Participant funnel through inclusion criteria") %>%
  kable_classic(full_width = T, html_font = "Cambria") 
```


## Summarize unmatched data
Prior to conducting matching, we examined key risk characteristics of the pool of potential study participants. From this table, we can see that prior to match, the Spring group consisted of slightly more women, more individuals in the 25-44 age category, had slightly lower medical spending risk scores, and comparatively more mood and anxiety diagnoses and fewer substance use diagnoses.

``` {r summary}
df_unmatched_table <- df_analyze_all %>%
  filter(index_date >= spring_start_date) %>%
  #mutate(cc_hier = case_when(cc_any == "no" ~ "none"
  #                           , cc_cancer == "yes" ~ "Cancer"
  #                           , cc_stroke == "yes" ~ "Stroke"
  #                           , cc_diabetes == "yes" ~ "Diabetes"
  #                           , cc_hypertension == "yes" ~ "Hypertension"
  #                           , cc_heart == "yes" ~ "Heart Disease"
  #                           , cc_kidney == "yes" ~ "Kidney Disease"
   #                          , cc_asthma_copd == "yes" ~ "Asthma and COPD"
   #                          , cc_osteo == "yes" ~ "Osteoporosis"
   #                          , TRUE ~ "none"
                             
  #)) %>%
  group_by(carrier_member_id, spring_dummy, age_at_index, member_sex, cc_any, cc_asthma_copd, cc_diabetes, cc_hypertension, cc_heart, cc_stroke, cc_kidney, cc_osteo, cc_cancer) %>%
  arrange(month_year) %>%
  summarize(
    carrier_mh_dx = first(carrier_primary_mh_dx, na_rm = TRUE),
    spring_mh_dx = first(spring_primary_mh_dx, na_rm = TRUE),
    risk_score_dx = risk_score[months == 1]
  ) %>%
  ungroup() %>%
  mutate(mh_dx = coalesce(spring_mh_dx, carrier_mh_dx)) %>%
  mutate(dx_collapsed = fct_collapse(mh_dx,
                                   mood = "mood",
                                   anxiety = "anxiety",
                                   sud = "sud",
                                   other = c("personality", "psychotic", "intellectual disability", "physical behavioral", "physiological", "developmental", "child onset", "unspecified")
  )) %>%
  select(-c(carrier_mh_dx, spring_mh_dx)) %>%
  ungroup()

## Examine overall table
### NOTE: p-value function is broken so currently dropping
table1( ~ age_at_index + member_sex + mh_dx + dx_collapsed + risk_score_dx + cc_any + cc_asthma_copd + cc_diabetes + cc_hypertension + cc_heart
        + cc_stroke + cc_kidney + cc_osteo + cc_cancer | spring_dummy,
        overall = F,
        data=df_unmatched_table)
```

  
  
  
## Summarize matched data
We matched on age, sex, mental health diagnosis, and medical spending risk scores (Department of Health and Human Services - Hierarchal Condition Categories - platinum tier). We matched on a ratio to include as many relevant participants from the comparison condition as possible. In total, we matched X spring participants to Y participants in the comparison group. After matching, the groups were essentially identical across all key characteristics. 

``` {r compare-match-groups}
df_match_table <- df_matched %>%
  group_by(carrier_member_id) %>%
  arrange(months) %>%
  mutate(
    therapy_sessions_cum = case_when(
      spring_dummy == "Spring" ~ cumsum(spring_therapist_count_month),
      spring_dummy == "Health Plan" ~ cumsum(carrier_therapist_count_month)
    )
  ) %>%
  mutate(therapy_sessions_total = max(therapy_sessions_cum, na.rm=T)) %>%
  group_by(carrier_member_id, cc_any, cc_asthma_copd, cc_diabetes, cc_hypertension, cc_heart, cc_stroke, cc_kidney, cc_osteo, cc_cancer) %>%
  arrange(months) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(date_rank = dense_rank(index_date)) %>%
  mutate(index_date = format(index_date, "%b %Y")) %>%
  mutate(index_date = fct_reorder(factor(index_date), date_rank)) %>%
  mutate(spring_dummy = factor(spring_dummy, labels = c("Control", "Spring Health"))) 
  


# Add labels
label(df_match_table$age_at_index) <- "Age"
label(df_match_table$member_sex) <- "Sex (assigned at birth)"
label(df_match_table$dx_imputed) <- "Mental health diagnosis"
label(df_match_table$risk_score_dx) <- "Risk score at time of diagnosis"
label(df_match_table$index_date) <- "Month of diagnosis"
label(df_match_table$therapy_sessions_total) <- "Number of therapy sessions"

# NOTE: p-value function is broken here so currently dropping
table1( ~ age_at_index + member_sex + dx_imputed + risk_score_dx + cc_any + cc_asthma_copd + cc_diabetes + cc_hypertension + cc_heart
        + cc_stroke + cc_kidney + cc_osteo + cc_cancer | spring_dummy,
        overall = F,
        footnote = "This table is based on raw values. In cases where 2 matches were not achieved, weights were applied.",
        data=df_match_table)


# Drop median, min, max
render.cont <- function(x) {
    with(stats.apply.rounding(stats.default(round(x, 1)), digits=3), c("",
        "Mean (SD)"=sprintf("%s (%s)", MEAN, SD)))
}

table1( ~ age_at_index + member_sex + dx_imputed + risk_score_dx + therapy_sessions_total | spring_dummy,
        overall = F,
        render.continuous = render.cont,
        footnote = "This table is based on raw values. In cases where 2 matches were not achieved, weights were applied.",
        data=df_match_table)


# This is better with p-values but formatting is ugly
library(survey)
library(tableone)
t1_design <- svydesign(ids = ~carrier_member_id, strata = ~spring_dummy, weights = ~weights_nn,
                       nest = TRUE, data = df_match_table)

t1 <- svyCreateTableOne(
  vars = c("age_at_index", "member_sex", "dx_imputed", "risk_score_dx", "index_date"), 
  strata = "spring_dummy", 
  data = t1_design) 

t1 %>%
  kableone() %>%
  kable_classic(full_width = FALSE, html_font = "Cambria") %>%
  remove_column(5)
```

  
# Outcome models
## Spring effect on gross medical spending
Below are the results of the total cost of care study across the entire population and the matched group only.
``` {r gross-spend, fig.width = 9, fig.height = 5}

# Let's recode customer so the intercept reflects the average across participants
cust_recode <- df_matched %>%
  group_by(customer_name) %>%
  summarize(cust_row_count = n()) %>%
  ungroup() %>%
  mutate(cust_prop = cust_row_count/sum(cust_row_count)) %>%
  select(customer_name, cust_prop) %>%
  pivot_wider(names_from = customer_name, values_from = cust_prop) 

df_matched <- df_matched %>%
  mutate(
    Hearst = ifelse(customer_name == "Hearst", 1, 0),
    Pepsi = ifelse(customer_name == "Pepsi", 1, 0),
    Tegna = ifelse(customer_name == "Tegna", 1, 0),
    Wellstar = ifelse(customer_name == "Wellstar", 1, 0),
    DocuSign = ifelse(customer_name == "DocuSign", 1, 0)
  )

df_analyze_all <- df_analyze_all %>%
  mutate(
    Hearst = ifelse(customer_name == "Hearst", 1, 0),
    Pepsi = ifelse(customer_name == "Pepsi", 1, 0),
    Tegna = ifelse(customer_name == "Tegna", 1, 0),
    Wellstar = ifelse(customer_name == "Wellstar", 1, 0),
    DocuSign = ifelse(customer_name == "DocuSign", 1, 0)
  )


## Gross
m1_gross_no_match <- lmer(med_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase + Hearst + Pepsi + Tegna + Wellstar +
             (1 | carrier_member_id),
           data = filter(df_analyze_all, index_date >= spring_start_date))

m1_gross_yes_match <- lmer(med_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase + Hearst + Pepsi + Tegna + Wellstar +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m1_gross_exclusions <- lmer(med_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase + Hearst + Pepsi + Tegna + Wellstar +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = filter(df_matched, excl_pregnancy != "yes"))

tab_model(m1_gross_no_match, m1_gross_yes_match, m1_gross_exclusions, 
          show.ci=F, 
          show.se=T, 
          pred.labels = c("Baseline PMPM", "Baseline difference (Spring - Control)", "Control pre-post change", "Hearst", "Pepsi", "Tegna", "Wellstar", "Diff-in-diff (Spring change - Control change)"),
          dv.labels = c("Umatched", "Matched", "Exclude pregnancy"),
          title = "Spring effect on gross medical spending")
# raw with bootstrapped SEs. 
# Use residuals because we trust the shape of the regression (all binary) but not the noise
#m1_boot <- bootstrap(m1_nn_gross, .f = fixef, type = "residual", B = 2000)
#summary(m1_boot)
```


## Plot spring effect on gross spend
``` {r plot-med-spending-results, fig.width = 6, fig.height = 4}
df_plot <- df_matched %>%
  distinct(spring_dummy, phase) %>%
  cbind(cust_recode) %>%
  mutate(
    phase_label = case_when(
      phase == "pre_tx" ~ "Before MH diagnosis",
      phase == "post_tx" ~ "After MH diagnosis"
    )
  ) %>%
  mutate(phase_label = factor(phase_label, levels = c("Before MH diagnosis", "After MH diagnosis")))

df_plot <- predictions(m1_gross_yes_match, newdata = df_plot, re.form = ~0)

color_scheme <- c('#c7c7c7', "#37837c")

# Control only
df_plot_control <- filter(df_plot, spring_dummy == "Health Plan")
ggplot(df_plot_control, aes(x=phase_label, y=estimate, ymin=conf.low, ymax=conf.high, group = spring_dummy, color = spring_dummy)) +
  geom_point(size=3) +
  geom_line() +
  scale_color_manual(values = color_scheme, labels = c("Control", "Spring Health")) +
  geom_text_repel(aes(label=round(estimate, 0)), hjust = ifelse(df_plot_control$phase_label == "Before MH diagnosis", 1.4, -0.4)) +
  theme_modern() +
  theme(legend.position = "bottom") +
  labs(
    title = "Control group spending before and after MH diagnosis",
    x = "",
    y = "PMPM allowed amount",
    color = ""
  )

# Overall, no error bars
ggplot(df_plot, aes(x=phase_label, y=estimate, ymin=conf.low, ymax=conf.high, group = spring_dummy, color = spring_dummy)) +
  geom_point(size=3) +
  geom_line() +
  scale_color_manual(values = color_scheme, labels = c("Control", "Spring Health")) +
  geom_text_repel(aes(label=round(estimate, 0)), hjust = ifelse(df_plot$phase_label == "Before MH diagnosis", 1.4, -0.4)) +
  theme_modern() +
  theme(legend.position = "bottom") +
  labs(
    title = "Spend trajectories for Spring Health versus control group",
    x = "",
    y = "PMPM allowed amount",
    color = ""
  )

# Overall with error bars
ggplot(df_plot, aes(x=phase_label, y=estimate, ymin=conf.low, ymax=conf.high, group = spring_dummy, color = spring_dummy)) +
  geom_errorbar(width = 0.05) +
  geom_point(size=3) +
  geom_line() +
  scale_color_manual(values = color_scheme, labels = c("Control", "Spring Health")) +
  geom_text_repel(aes(label=round(estimate, 0)), hjust = ifelse(df_plot$phase_label == "Before MH diagnosis", 1.4, -0.4)) +
  theme_modern() +
  theme(legend.position = "bottom") +
  labs(
    title = "Spend trajectories for Spring Health versus control group",
    x = "",
    y = "PMPM allowed amount",
    color = ""
  )
```

## Spring impact at participant 1-year follow-up
``` {r 1-yr-follow-up}
m_1yr_participant <- lmer(med_pmpm_trunc ~ 1 + spring_dummy + as.factor(months_post) +
                          spring_dummy*as.factor(months_post) + 
                             (1 | carrier_member_id) +
                             (1 | subclass_nn),
                           weights = weights_nn,
                           data = df_matched)

tab_model(m_1yr_participant, show.ci=F, show.se=T)

# Get PPPY in dollars
hypotheses(m_1yr_participant, hypothesis = "b15 + b16 + b17 + b18 + b19 + b20 + b21 + b22 + b23 + b24 + b25 + b26 = 0")

# Get PPPY in pct
hypotheses(m_1yr_participant, hypothesis = "(b15 + b16 + b17 + b18 + b19 + b20 + b21 + b22 + b23 + b24 + b25 + b26) /
          (b1*12 + b3 + b4 + b5 + b6 + b7 + b8 + b9 + b10 + b11 + b12 + b13 + b14)  = 0")

```
  
  
## Spring effect on Rx
``` {r model-rx-spend, fig.width = 9, fig.height = 5}

# Only run rx models if client has rx data
## No matching
m1_rx_no_match <- lmer(rx_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase + customer_name +
             (1 | carrier_member_id),
           data = filter(df_analyze_all, index_date >= spring_start_date))

## Matching
m1_rx_yes_match <- lmer(rx_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase + customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

tab_model(m1_rx_no_match, m1_rx_yes_match, show.ci=F, show.se=T, 
          pred.labels = c("Baseline PMPM", "Baseline difference (Spring - Control)", "Control pre-post change", "Diff-in-diff (Spring change - Control change)"),
          dv.labels = c("Umatched", "Matched", "Exclude pregnancy"),
          title = "Spring effect on gross pharmacy spending")

```


## Chronic conditions
``` {r chronic-condition-modeling}

# Aggregate by mental health spend
df_matched <- df_matched %>%
  mutate(
    med_pmpm_trunc_mh = 
      med_pmpm_trunc_therapy_mh + 
      med_pmpm_trunc_ov_mh + 
      med_pmpm_trunc_er_mh + 
      med_pmpm_trunc_ip_mh + 
      med_pmpm_trunc_hosp_op_mh + 
      med_pmpm_trunc_other_mh,
    med_pmpm_trunc_nonmh = 
      med_pmpm_trunc_therapy_nonmh + 
      med_pmpm_trunc_ov_nonmh + 
      med_pmpm_trunc_er_nonmh + 
      med_pmpm_trunc_ip_nonmh + 
      med_pmpm_trunc_hosp_op_nonmh + 
      med_pmpm_trunc_other_nonmh
  )

# Model
m1 <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_diabetes + cc_diabetes*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m2 <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_hypertension + cc_hypertension*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m3 <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_asthma_copd + cc_asthma_copd*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m4 <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_kidney + cc_kidney*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m5 <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_osteo + cc_osteo*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m6 <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
             excl_pregnancy + excl_pregnancy*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m7 <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_cancer + cc_cancer*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m8 <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_diabetes + cc_diabetes*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m9 <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_hypertension + cc_hypertension*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m10 <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_asthma_copd + cc_asthma_copd*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m11 <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_kidney + cc_kidney*(spring_dummy + spring_dummy*phase) +
              customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m12 <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_osteo + cc_osteo*(spring_dummy + spring_dummy*phase) +
              customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m13 <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
             excl_pregnancy + excl_pregnancy*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m14 <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
             cc_cancer + cc_cancer*(spring_dummy + spring_dummy*phase) +
             customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m_all_mh <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
                   customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

m_all_nonmh <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
                      customer_name +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)


m_list <- list(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14)
df_cc_results <- data.frame(
  Term = NA, 
  Estimate = NA, 
  se = NA, 
  z = NA, 
  p = NA, 
  lb = NA, 
  ub = NA)

for (i in 1:length(m_list)) {
  df_cc_results[i,] <- hypotheses(m_list[[i]], hypothesis = "b9 + b12 = 0")
  df_cc_results[15,] <- hypotheses(m_all_mh, hypothesis = "b8 = 0") # add pop average MH
  df_cc_results[16,] <- hypotheses(m_all_nonmh, hypothesis = "b8 = 0") # add pop average non-MH
}

# Add cc names
df_cc_results <- df_cc_results %>%
  mutate(
    chronic_condition = c(
      rep(c("Diabetes", "Hypertension", "Asthma/COPD", "Kidney disease", "Osteoporosis", "Pregnancy", "Cancer"), 2),
      rep("Population average", 2)
      ),
    var_name = c(
      rep(c("cc_diabetes", "cc_hypertension", "cc_asthma_copd", "cc_kidney", "cc_osteo", "excl_pregnancy", "cc_cancer"), 2),
      rep("Population average", 2)
    ),
    spend_type = c(rep("Mental healthcare savings", 7), rep("All other healthcare savings", 7), "Mental healthcare savings", "All other healthcare savings")
  )

# Add Ns
df_cc_results <- df_cc_results %>%
  left_join(
    df_matched %>% 
      select(carrier_member_id, spring_dummy, any_of(df_cc_results$var_name)) %>%
      group_by(spring_dummy) %>%
      summarize(across(everything(), ~ n_distinct(carrier_member_id[.x == "yes"]))) %>%
      select(-carrier_member_id) %>%
      pivot_longer(-spring_dummy, names_to = "var_name", values_to = "N") %>%
      pivot_wider(id_cols = var_name, names_from = spring_dummy, values_from = N, names_prefix = "N from ")
  ) %>%
  mutate(
    "N from Health Plan" = case_when(
      chronic_condition == "Population average" ~ n_distinct(df_matched$carrier_member_id[df_matched$spring_dummy == "Health Plan"]),
      TRUE ~ `N from Health Plan`
    ),
    "N from Spring" = case_when(
      chronic_condition == "Population average" ~ n_distinct(df_matched$carrier_member_id[df_matched$spring_dummy == "Spring"]),
      TRUE ~ `N from Spring`
    )
  ) %>%
  relocate(chronic_condition, `N from Spring`, `N from Health Plan`) %>%
  select(-c(Term, var_name, z))
```


``` {r plot-chronic-conditions}

## Make it nice
cc_colors <- c("#34a853", "grey")
df_plot_cc <- df_cc_results %>%
  mutate(
    Estimate = -1*Estimate,
    lb = -1*lb,
    ub = -1*ub
  ) %>%
  mutate(
    chronic_condition = fct_reorder(as.factor(chronic_condition), Estimate),
    spend_type = fct_relevel(spend_type,"Mental healthcare savings", "All other healthcare savings")
    )

## Let's plot with CIs so we can understand it
ggplot(df_plot_cc, aes(x=Estimate, xmin=lb, xmax=ub, y=chronic_condition, color = spend_type)) +
  geom_pointrange(position = position_dodge(width=0.5)) +
  scale_color_manual(values = cc_colors) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme_modern() +
  theme(legend.position = "bottom")


## For barplot, we want overall value laels
df_labels <- df_plot_cc %>%
  group_by(chronic_condition) %>%
  summarize(total = sum(Estimate)) 


ggplot(df_plot_cc, aes(x=Estimate, y=chronic_condition, fill = spend_type)) +
  geom_bar(stat = "identity", width = 0.6, position=position_stack(reverse=T)) +
  scale_fill_manual(values = cc_colors) +
  geom_text(aes(x=total, y=chronic_condition, label = round(total, 0), fill = NULL, hjust = ifelse(total < 0, 1.1, -0.4)), colour = "#8e8e8e", size = 3, data = df_labels) +
  expand_limits(x=c(0, 1.1*max(df_labels$total))) +
  theme_modern() +
  theme(legend.position = "bottom") +
  labs(
    x = "PMPM savings",
    y = "",
    fill = " "
  )


## Add donut chart *gag* 
# Compute percentages
df_donut <- df_plot_cc %>%
  filter(chronic_condition == "Population average") %>%
  group_by(spend_type) %>%
  summarize(total = sum(Estimate)) %>%
  ungroup() %>%
  mutate(fraction = total / sum(total)) %>%
  mutate(
    ymax = cumsum(fraction),
    ymin = c(0, head(ymax, n=-1))
    ) %>%
  mutate(labelPosition = (ymax + ymin) /2)


# Make the plot
ggplot(df_donut, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=spend_type)) +
     geom_rect() +
     coord_polar(theta="y") + 
     xlim(c(2, 4)) +
  theme_modern() +
  theme_void() +
  scale_fill_manual(values = cc_colors) + 
  geom_text(aes(x=3.5, y=labelPosition, label=paste0(100*round(df_donut$fraction, 2), "%")), fontface = "bold") +
  labs(fill = "") +
  theme(legend.position = "bottom")

```


## Outcomes by MH disorder
``` {r -outcomes-by-disorder}

# Models
sud_overall <- lmer(med_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase + 
                             (1 | carrier_member_id) +
                             (1 | subclass_nn),
                           #weights = weights_nn,
                           data = filter(df_matched, dx_imputed == "sud"))


mh_mood <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase +
                       (1 | carrier_member_id) +
                       (1 | subclass_nn),
                     weights = weights_nn,
                     data = filter(df_matched, dx_imputed == "mood"))

mh_anxiety <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
                        (1 | carrier_member_id) +
                        (1 | subclass_nn),
                      weights = weights_nn,
                      data = filter(df_matched, dx_imputed == "anxiety"))

mh_sud <- lmer(med_pmpm_trunc_mh ~ 1 + spring_dummy + spring_dummy*phase + 
                             (1 | carrier_member_id) +
                             (1 | subclass_nn),
                           #weights = weights_nn,
                           data = filter(df_matched, dx_imputed == "sud"))

nonmh_mood <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
                       (1 | carrier_member_id) +
                       (1 | subclass_nn),
                     weights = weights_nn,
                     data = filter(df_matched, dx_imputed == "mood"))

nonmh_anxiety <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
                        (1 | carrier_member_id) +
                        (1 | subclass_nn),
                      weights = weights_nn,
                      data = filter(df_matched, dx_imputed == "anxiety"))

nonmh_sud <- lmer(med_pmpm_trunc_nonmh ~ 1 + spring_dummy + spring_dummy*phase + 
                             (1 | carrier_member_id) +
                             (1 | subclass_nn),
                           #weights = weights_nn,
                           data = filter(df_matched, dx_imputed == "sud"))

dx_list <- list(mh_mood, mh_anxiety, mh_sud, nonmh_mood, nonmh_anxiety, nonmh_sud)

df_dx_results <- data.frame(
  Term = NA, 
  Estimate = NA, 
  se = NA, 
  z = NA, 
  p = NA, 
  lb = NA, 
  ub = NA)

for (i in 1:length(dx_list)) {
  df_dx_results[i,] <- hypotheses(dx_list[[i]], hypothesis = "b4 = 0")
  df_dx_results[7,] <- hypotheses(m_all_mh, hypothesis = "b8 = 0") # add pop average MH
  df_dx_results[8,] <- hypotheses(m_all_nonmh, hypothesis = "b8 = 0") # add pop average non-MH
}

# Add cc names
df_dx_results <- df_dx_results %>%
  mutate(
    mh_diagnosis = c(
      rep(c("Mood", "Anxiety", "SUD"), 2),
      rep("Population average", 2)
      ),
    var_name = c(
      rep(c("mood", "anxiety", "sud"), 2),
      rep("Population average", 2)
    ),
    spend_type = c(rep("Mental healthcare savings", 3), rep("All other healthcare savings", 3), "Mental healthcare savings", "All other healthcare savings")
  )

```


## Plot MH disorders
``` {r plot-dx}

## Make it nice
cc_colors <- c("#34a853", "grey")
df_plot_dx <- df_dx_results %>%
  mutate(
    Estimate = -1*Estimate,
    lb = -1*lb,
    ub = -1*ub
  ) %>%
  mutate(
    mh_diagnosis = fct_reorder(as.factor(mh_diagnosis), Estimate),
    spend_type = fct_relevel(spend_type,"Mental healthcare savings", "All other healthcare savings")
    )

## Let's plot with CIs so we can understand it
ggplot(df_plot_dx, aes(x=Estimate, xmin=lb, xmax=ub, y=mh_diagnosis, color = spend_type)) +
  geom_pointrange(position = position_dodge(width=0.5)) +
  scale_color_manual(values = cc_colors) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme_modern() +
  theme(legend.position = "bottom")


## For barplot, we want overall value laels
df_labels <- df_plot_dx %>%
  group_by(mh_diagnosis) %>%
  summarize(total = sum(Estimate)) 


# Bar plot
ggplot(df_plot_dx, aes(x=Estimate, y=mh_diagnosis, fill = spend_type)) +
  geom_bar(stat = "identity", width = 0.6, position=position_stack(reverse=T)) +
  scale_fill_manual(values = cc_colors) +
  geom_text(aes(x=total, y=mh_diagnosis, label = round(total, 0), fill = NULL, hjust = ifelse(total < 0, 1.1, -0.4)), colour = "#8e8e8e", size = 3, data = df_labels) +
  expand_limits(x=c(0, 1.1*max(df_labels$total))) +
  theme_modern() +
  theme(legend.position = "bottom") +
  labs(
    x = "PMPM savings",
    y = "",
    fill = " "
  )


# Line plot
#df_plot_sud <- df_matched %>%
#  distinct(spring_dummy, phase) %>%
#  mutate(
#    phase_label = case_when(
#      phase == "pre_tx" ~ "Before MH diagnosis",
#      phase == "post_tx" ~ "After MH diagnosis"
#    )
#  ) %>%
#  mutate(phase_label = factor(phase_label, levels = c("Before MH diagnosis", "After MH diagnosis")))
#
#df_plot_sud <- predictions(m1_gross_yes_match, newdata = df_plot, re.form = ~0)
#
#color_scheme <- c('#c7c7c7', "#37837c")
#
#
## Overall with error bars
#ggplot(df_plot, aes(x=phase_label, y=estimate, ymin=conf.low, ymax=conf.high, group = spring_dummy, color = spring_dummy)) +
#  geom_errorbar(width = 0.05) +
#  geom_point(size=3) +
#  geom_line() +
#  scale_color_manual(values = color_scheme, labels = c("Control", "Spring Health")) +
#  geom_text_repel(aes(label=round(estimate, 0)), hjust = ifelse(df_plot$phase_label == "Before MH diagnosis", 1.4, -0.4)) +
#  theme_modern() +
#  theme(legend.position = "bottom") +
#  labs(
#    title = "Spend trajectories for Spring Health versus control group",
#    x = "",
#    y = "PMPM allowed amount",
#    color = ""
#  )

```



## Cost categories
``` {r cost-categories}
cc1 <- lmer(med_pmpm_trunc_ov_mh ~ 1 + spring_dummy + spring_dummy*phase +
              customer_name +
              (1 | carrier_member_id) +
              (1 | subclass_nn),
            weights = weights_nn,
            data = df_matched)

cc2 <- lmer(med_pmpm_trunc_er_mh ~ 1 + spring_dummy + spring_dummy*phase +
              customer_name +
              (1 | carrier_member_id) +
              (1 | subclass_nn),
            weights = weights_nn,
            data = df_matched)

cc3 <- lmer(med_pmpm_trunc_hosp_op_mh ~ 1 + spring_dummy + spring_dummy*phase +
              customer_name +
              (1 | carrier_member_id) +
              (1 | subclass_nn),
            weights = weights_nn,
            data = df_matched)

cc4 <- lmer(med_pmpm_trunc_ip_mh ~ 1 + spring_dummy + spring_dummy*phase +
              customer_name +
              (1 | carrier_member_id) +
              (1 | subclass_nn),
            weights = weights_nn,
            data = df_matched)

## Non-MH
cc5 <- lmer(med_pmpm_trunc_ov_nonmh ~ 1 + spring_dummy + spring_dummy*phase +
              customer_name +
              (1 | carrier_member_id) +
              (1 | subclass_nn),
            weights = weights_nn,
            data = df_matched)

cc6 <- lmer(med_pmpm_trunc_er_nonmh ~ 1 + spring_dummy + spring_dummy*phase +
              customer_name +
              (1 | carrier_member_id) +
              (1 | subclass_nn),
            weights = weights_nn,
            data = df_matched)

cc7 <- lmer(med_pmpm_trunc_hosp_op_nonmh ~ 1 + spring_dummy + spring_dummy*phase +
              customer_name +
              (1 | carrier_member_id) +
              (1 | subclass_nn),
            weights = weights_nn,
            data = df_matched)

cc8 <- lmer(med_pmpm_trunc_ip_nonmh ~ 1 + spring_dummy + spring_dummy*phase +
              customer_name +
              (1 | carrier_member_id) +
              (1 | subclass_nn),
            weights = weights_nn,
            data = df_matched)


# Make in table
df_cost_results <- data.frame(
  outcome = rep(c("Office visits", "Emergency room", "Hospital outpatient", "Hospital inpatient"), 2),
  spend_type = c(rep("Mental healthcare savings", 4), rep("All other healthcare savings", 4)),
  estimate = NA,
  se = NA
) %>%
  mutate(outcome = fct_relevel(as.factor(outcome), "Office visits", "Emergency room", "Hospital outpatient", "Hospital inpatient"))

for (i in 1:8) {
  df_cost_results$estimate[i] = summary(get(paste0("cc", i)))$coefficients["spring_dummySpring:phasepost_tx", "Estimate"]
  df_cost_results$se[i] = summary(get(paste0("cc", i)))$coefficients["spring_dummySpring:phasepost_tx", "Std. Error"]
}

df_cost_results %>%
  group_by(outcome) %>%
  summarize(total = sum(estimate)) %>%
  mutate(total = round(total, 0)) 


df_donut_cc <- df_cost_results %>%
  group_by(outcome) %>% 
  mutate(fraction = estimate/sum(estimate)) %>%
  mutate(
    ymax = cumsum(fraction),
    ymin = c(0, head(ymax, n=-1))
    ) %>%
  ungroup() %>%
  mutate(labelPosition = (ymax + ymin) /2) %>%
  mutate(spend_type = fct_relevel(spend_type,"Mental healthcare savings", "All other healthcare savings"))


# Make the plots
donut_list <- list()
outcome_list <- unique(df_donut_cc$outcome)

for (i in 1:length(outcome_list)) {
donut_list[[i]] <- ggplot(filter(df_donut_cc, outcome == outcome_list[[i]]), aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=spend_type)) +
     geom_rect() +
     coord_polar(theta="y") + 
     xlim(c(2, 4)) +
  scale_fill_manual(values = cc_colors) + 
  theme_modern() +
  theme_void() +
  theme(legend.position = "none") +
  labs(fill = "")
}


# Make the table
df_donut_cc %>%
  group_by(outcome) %>%
  summarize(total = -1*sum(estimate)) %>%
  mutate(Description = c(
    "Less mental health care delivered in an inappropriate setting by primary care providers",
    "Lower utilization of high-cost emerency room services",
    "Getting patients the mental health care they need decreases excess outpatient medical spending",
    "Greater adherence to care plans keeps Spring patients out of the hospital setting, where diagnostic tests and high-cost procedures can drive unnecessary spend"
  )) %>%
  mutate(total = scales::dollar_format()(round(total, 0))) %>%
  mutate("% Savings from mental health" = NA) %>% # Make placeholder for plot
  rename(
    "Service category" = outcome,
    "PMPM savings" = total
  ) %>%
  relocate(Description, .after = "Service category") %>%
  tibble() %>%
  gt() %>%
   text_transform(
    locations = cells_body(columns = `% Savings from mental health`),
    fn = function(x) {
      donut_list %>%
        ggplot_image(height = px(80))
    }
  ) %>%
  tab_options(column_labels.font.weight = "bold") %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_column_labels()
    ) %>%
  tab_style(
    style = cell_text(weight = "bold"), 
    locations = cells_body(columns = c("Service category", "PMPM savings"))
)
```

## Therapy moderators

``` {r therapy-moderators}

# Calculate cumulative sessions
df_matched <- df_matched %>%
  group_by(carrier_member_id) %>%
  arrange(months) %>%
  mutate(
    therapy_sessions = case_when(
      spring_dummy == "Spring" ~ cumsum(spring_therapist_count_month),
      spring_dummy == "Health Plan" ~ cumsum(carrier_therapist_count_month)
    )
  ) %>%
  mutate(therapy_sessions_total = max(therapy_sessions, na.rm=T))

m_sessions1 <- lmer(med_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase + Hearst + Pepsi + Tegna + Wellstar +
                     therapy_sessions +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

## Should be different for Spring because spring sessions are not included in med spending costs
m_sessions2 <- lmer(med_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase + Hearst + Pepsi + Tegna + Wellstar +
                     therapy_sessions*spring_dummy +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

## Should be different for Spring because spring sessions are not included in med spending costs
m_sessions3 <- lmer(med_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase + Hearst + Pepsi + Tegna + Wellstar +
                     therapy_sessions_total*phase*spring_dummy +
             (1 | carrier_member_id) +
             (1 | subclass_nn),
           weights = weights_nn,
           data = df_matched)

tab_model(m_sessions1, m_sessions2, show.ci=F, show.se=T)

```

## Trajectories

``` {r trajectory-splines}
library(splines)


# Fit models
m1_spline <- lmer(med_pmpm_trunc ~ 1 + spring_dummy + spring_dummy*phase +
                    spring_dummy*(ns(months_post, df = 4)) +
                    (1 | carrier_member_id) +
                    (1 | subclass_nn),
                  weights = weights_nn,
                  data = df_matched)

df_pred <- df_matched %>%
  distinct(spring_dummy, phase, months, months_post)

  df_plot_splines <- predictions(
    m1_spline,
    newdata = df_pred,
    re.form = ~0)
 

# Plot raw
df_matched %>%
  group_by(spring_dummy, months) %>%
  summarize(
    pmpm = mean(med_pmpm_trunc, na.rm=T),
    sd = sd(med_pmpm_trunc, na.rm=T),
    n = n_distinct(carrier_member_id),
    se = sd/sqrt(n)
    ) %>%
  filter(months <= 12) %>%
  ggplot(., aes(x=months, y=pmpm, ymin = pmpm - 1.96*se, ymax = pmpm + 1.96*se, group = spring_dummy, color=spring_dummy)) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_pointrange() +
  geom_line() +
  theme_modern() +
  theme(
    legend.position = "none",
    strip.text.x = element_blank()
    ) +
  labs(title = "Gross ROI")

## Approximate net ROI
df_matched %>%
  group_by(spring_dummy, months) %>%
  summarize(
    pmpm = mean(med_pmpm_trunc_net, na.rm=T),
    sd = sd(med_pmpm_trunc, na.rm=T),
    n = n_distinct(carrier_member_id),
    se = sd/sqrt(n)
    ) %>%
  filter(months <= 12) %>%
  ggplot(., aes(x=months, y=pmpm, ymin = pmpm - 1.96*se, ymax = pmpm + 1.96*se, group = spring_dummy, color=spring_dummy)) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_pointrange() +
  geom_line() +
  scale_color_manual(values = rev(cc_colors), labels = c("Control", "Spring Health")) +
  theme_modern() +
  theme(
    legend.position = "none",
    strip.text.x = element_blank()
    ) +
  labs(
    x = "Months from Spring launch",
    y = "PMPM ($)",
    title = "Net ROI approximation")

# Plot splines
ggplot(df_plot_splines, aes(x=months, y=estimate, ymin = conf.low, ymax=conf.high, group = spring_dummy, color=spring_dummy)) +
  geom_line() +
  geom_pointrange() +
  theme_modern() +
  theme(
    legend.position = "none",
    strip.text.x = element_blank(),
    title = "Gross ROI"
  )

```

``` {r monthly-cc-breakdown, fig.width=7, fig.height=7}

df_monthly_spend <- df_matched %>%
  mutate(med_pmpm_trunc_ov_mh = med_pmpm_trunc_ov_mh + 195*spring_tx_count_month) %>% # spring spending not yet included here
  group_by(spring_dummy, months) %>%
  summarize(
    pmpm_mh_ov = mean(med_pmpm_trunc_ov_mh, na.rm=T),
    pmpm_mh_er = mean(med_pmpm_trunc_er_mh, na.rm=T),
    pmpm_mh_op = mean(med_pmpm_trunc_hosp_op_mh, na.rm=T),
    pmpm_mh_ip = mean(med_pmpm_trunc_ip_mh, na.rm=T),
    
    pmpm_nonmh_ov = mean(med_pmpm_trunc_ov_nonmh, na.rm=T),
    pmpm_nonmh_er = mean(med_pmpm_trunc_er_nonmh, na.rm=T),
    pmpm_nonmh_op = mean(med_pmpm_trunc_hosp_op_nonmh, na.rm=T),
    pmpm_nonmh_ip = mean(med_pmpm_trunc_ip_nonmh, na.rm=T)
    ) %>%
  filter(months <= 12) %>%
  filter(months > 0) %>%
  pivot_longer(
    cols = c(pmpm_mh_ov:pmpm_nonmh_ip),
    names_prefix = "pmpm_",
    names_to = "spend_cat",
    values_to = "estimate"
    ) %>%
  mutate(
    mh_spend = ifelse(str_starts(spend_cat, "mh_*"), "mh", "non-MH"),
    category = str_replace(spend_cat, ".*_", "")
  ) %>%
  mutate(
    mh_spend = ifelse(mh_spend == "mh", "Mental Health spend", "Non-MH spend"),
    category = case_when(
      category == "er" ~ "ER",
      category == "ip" ~ "Inpatient",
      category == "op" ~ "Outpatient",
      category == "ov" ~ "Office Visits"
    )
  ) %>%
  mutate(category = factor(category, levels = c("Office Visits", "ER", "Inpatient", "Outpatient")))

# Category level
ggplot(df_monthly_spend, aes(x=months, y=estimate, group = spring_dummy, fill = spring_dummy)) +
  geom_bar(stat = "identity", width = 0.6, position=position_dodge()) +
  scale_fill_manual(values = rev(cc_colors)) +
  #geom_text(aes(x=total, y=chronic_condition, label = round(total, 0), fill = NULL, hjust = ifelse(total < 0, 1.1, -0.4)), colour = "#8e8e8e", size = 3, data = df_labels) +
  #expand_limits(x=c(0, 1.1*max(df_labels$total))) +
  theme_modern() +
  facet_grid(rows=vars(category), cols=vars(mh_spend), scales = "fixed") +
  theme(legend.position = "bottom") +
  labs(
    title = "Monthly spend by service category",
    x = "Months after Spring launch",
    y = "PMPM savings",
    fill = " "
  )

# MH vs non-MH
df_monthly_spend %>%
  group_by(spring_dummy, months, mh_spend) %>%
  summarize(estimate = sum(estimate, na.rm=T)) %>%
  # Plot
  ggplot(., aes(x=months, y=estimate, group = spring_dummy, fill = spring_dummy)) +
  geom_bar(stat = "identity", width = 0.6, position=position_dodge()) +
  scale_fill_manual(values = rev(cc_colors)) +
  #geom_text(aes(x=total, y=chronic_condition, label = round(total, 0), fill = NULL, hjust = ifelse(total < 0, 1.1, -0.4)), colour = "#8e8e8e", size = 3, data = df_labels) +
  #expand_limits(x=c(0, 1.1*max(df_labels$total))) +
  theme_modern() +
  facet_grid(rows=vars(mh_spend), scales = "fixed") +
  theme(legend.position = "bottom") +
  labs(
    title = "Monthly spend for mental health and non-mental health conditions",
    x = "Months after Spring launch",
    y = "PMPM savings",
    fill = " "
  )

```

# ROI
## Billing data
``` {r billing-data}

# direct bill

## all direct bill appts
billing_appts <- readRDS('~/Library/CloudStorage/GoogleDrive-mhawrilenko@springhealth.com/Shared drives/ROI - Direct bill/HEOR clean/billing data.Rdata')

# Loop stuff
spring_fees <- list()
prop_matched <- vector()
for (i in 1:length(customer_name)) {
  
  ## Get covered life IDs for members in the study
spring_match_to_elig <- import(paste0(Sys.getenv("claims_folder_path"), "data/", customer_name[i], "/data_to_sba/", customer_name[i], "_", "eligibility_cls.csv")) %>%
  rename(any_of(c(
    carrier_member_id = "member_key",
    carrier_member_id = "indv_id",
    carrier_member_id = "individual_id"
  ))) %>%
  mutate(carrier_member_id = as.character(carrier_member_id)) %>%
  select(carrier_member_id, covered_life_id)


## Need members in the study
study_members <- df_matched %>%
  distinct(carrier_member_id, spring_dummy) %>%
  left_join(spring_match_to_elig)


## Match study members to their appts
apps_query <- "SELECT appointment_id, covered_life_id 
               FROM base_appointments 
               WHERE UPPER(customer_name) like ?"


apps <- dbGetQuery(con = snowflake_conn("base_layer"), apps_query, params = list(paste0('%', str_to_upper(customer_name[i]), '%'))) %>%
  clean_names()


## Calculate direct bill amounts by group
spring_start_date <- df_matched %>%
  filter(str_like(customer_name, paste0('%', .env$customer_name[i], '%'), ignore_case = TRUE)) %>%
  distinct(spring_start_date) %>%
  pull(spring_start_date) 

spring_end_date <- df_matched %>%
  filter(str_like(customer_name, paste0('%', .env$customer_name[i], '%'), ignore_case = TRUE)) %>%
  distinct(spring_end_date) %>%
  pull(spring_end_date) 

direct_bill <- billing_appts %>%
  filter(str_like(customer_name, paste0('%', .env$customer_name[i], '%'), ignore_case = TRUE)) %>% #.env$customer_name
  filter(month_of_service <= spring_end_date) %>%
  left_join(apps) %>% # get covered life id
  inner_join(study_members) %>% # only individuals included in the study
  ## sometimes an individual has multiple carrier member IDs. DOn't want duplicate billing. 
  ## so group by appointment_id and take first carrier_member_id
  group_by(appointment_id) %>% 
  filter(carrier_member_id == first(carrier_member_id) | is.na(carrier_member_id)) %>% # address billing data that gets duped
  ungroup() %>%
  summarize(amount = sum(total_billed, na.rm=T)) %>%
  pull(amount)


billing_all <- import(paste0(Sys.getenv("claims_folder_path"), "data/", customer_name[i], "/", customer_name[i], "_", "billing.xlsx")) %>%
  clean_names()

bundle_fee <- billing_all %>%
  filter(str_like(account, paste0('%', "bundle", '%'), ignore_case = TRUE)) %>%
  summarize(bundle_fee = sum(amount, na.rm=T)) %>%
  pull(bundle_fee)

platform_fee <- billing_all %>%
  filter(str_like(account, paste0('%', "platform", '%'), ignore_case = TRUE)) %>%
  summarize(platform_fee = sum(amount, na.rm=T)) %>%
  pull(platform_fee)

billed_to_health_plan <- readRDS(paste0(Sys.getenv("claims_folder_path"), "data/round_2_analysis/intermediate_data/", customer_name[i], "_spring_med_claims.Rdata")) %>%
  filter(month_year <= spring_end_date) %>%
  mutate(carrier_member_id = as.character(carrier_member_id)) %>%
  inner_join(study_members) %>%
  ungroup() %>%
  summarize(billed_to_health_plan = sum(allowed_amt, na.rm=T)) %>%
  pull(billed_to_health_plan)


## Get number of eligible employees on the health plan in the date range
elig <- readRDS(file = paste0(Sys.getenv("claims_folder_path"), "/data/round_2_analysis/intermediate_data/", customer_name[i], "_carrier_elig.Rdata")) %>%
  filter(month_year >= spring_start_date) %>%
  filter(month_year <= spring_end_date) %>%
  filter(employee_flag == "yes") 

## Get total employees
qry <- "SELECT DISTINCT a.customer_name, a.customer_id, id, dependent, b.created_at
                  FROM ds_trunk.base_layer.base_customers AS a
                  LEFT JOIN stitch_new.rotom_prod_replica.covered_lives AS b
                  ON a.customer_id = b.customer_id
                  WHERE UPPER(a.customer_name) LIKE ?
                  AND dependent = 'FALSE'
                  AND DATE(b.created_at) <= date(?)"

cl <- dbGetQuery(con = snowflake_conn("rotom"), qry, params = list(paste0('%', str_to_upper(customer_name[i]), '%'), spring_end_date)) %>%
  clean_names()

prop_on_health_plan[i] <- n_distinct(elig$carrier_member_id) / n_distinct(cl$id)

cust_funnel <- data_funnel %>%
  filter(customer_name == .env$customer_name[i]) 
prop_matched[i] <- pull(cust_funnel[7,4] / cust_funnel[1,4])

# Compile all fees
spring_fees[[i]] <- data.frame(
  fee_type = c("Bundle", "Platform", "Direct bill", "Billed to Health Plan")
) %>%
  mutate(
    customer_name = customer_name[i],
    prop_on_health_plan = prop_on_health_plan[i],
    prop_matched = prop_matched[i],
    Amount = case_when(
      fee_type == "Bundle" ~ bundle_fee * prop_on_health_plan[i] * prop_matched[i],
      fee_type == "Platform" ~ platform_fee * prop_on_health_plan[i] * prop_matched[i],
      fee_type == "Direct bill" ~ direct_bill,
      fee_type == "Billed to Health Plan" ~ billed_to_health_plan
    )
)
}
spring_fees <- spring_fees %>% bind_rows()

spring_fees %>%
  group_by(customer_name) %>%
  summarize(amount = sum(Amount, na.rm=T)) 

total_invoiced <- spring_fees %>%
  summarize(amount = sum(Amount, na.rm=T)) %>%
  pull(amount)
```

## Calculate ROI
``` {r calculate-roi}
df_roi <- df_matched %>%
  filter(spring_dummy == "Spring") %>%
  filter(month_year == first_spring_tx_date) %>%
  mutate(months_treated = interval(first_spring_tx_date, spring_end_date) %/% months(1) + 1) %>%
  group_by(months_treated) %>%
  summarize(n = n_distinct(carrier_member_id)) %>%
  mutate(
    member_months_treated = n*months_treated,
    month_roi_gross = n*months_treated*summary(m1_gross_yes_match)$coefficients["spring_dummySpring:phasepost_tx", 1])
mean_months_treated <- sum(df_roi$member_months_treated)/sum(df_roi$n)


# Calculate gross savings %
deltamethod(m1_gross_yes_match, "0 = (6.5*b8) / ((12-6.5)*df_plot$estimate[1] + 6.5*(df_plot$estimate[2]))")

# Calculate PPPY
deltamethod(m1_gross_yes_match, "0 = -1 * b8 * mean_months_treated")

# Calculate ROI multiple
deltamethod(m1_gross_yes_match, "0 = (-1*b8*(sum(df_roi$months_treated*df_roi$n)))/total_invoiced")
```



